Alone Together: Compositional Reasoning and Inference for Weak Isolation

### 2017-07-08 supplement.tex
Supplement with proofs

\section{Operational Semantics}

%\renewcommand{\ctxn}[3]{\C{TXN}_{#1}\langle #2 \rangle\{#3\}}
\begin{figure*}[!ht]
\raggedright
%
\textbf{Syntax}\\
%
\begin{smathpar}
\renewcommand{\arraystretch}{1.2}
\begin{array}{lclcl}
\multicolumn{5}{c} {
  {x,y} \in \mathtt{Variables}\qquad
  {f} \in \mathtt{Field\;Names} \qquad
% {\tau} \in \mathtt{Table\;Names}
  {i,j} \in \mathbb{N} \qquad
  {\odot} \in \{+,-,\le,\ge,=\}\qquad
  {k} \in \mathbb{Z}\cup\mathbb{B} \qquad
  {\rec} \in \{\bar{f}=\bar{k}\}\
}\\
{\stl,\stg,s} & \in & \mathtt{State} & \coloneqq &  \Pow{\{\bar{f}=\bar{k}\}} \\
{\I_e, \I_c }  & \in & \mathtt{Isolation Spec} & \coloneqq & (\stl,\stg,\stg') \rightarrow \Prop\\
v & \in & \mathtt{Values} & \coloneqq & k \ALT \rec \ALT s\\
e & \in & \mathtt{Expressions} & \coloneqq & k \ALT x \ALT x.f 
    \ALT \{\bar{f}=\bar{e}\} \ALT e_1 \odot e_2\\ 
c & \in & \mathtt{Commands} & \coloneqq & \cskip \ALT \lete{x}{e}{c}
    \ALT \ite{e}{c_1}{c_2}\ALT c_1;c_2 \ALT \inserte{x}  \\
&&&&\ALT \deletee{\lambda x.e}
    \ALT \lete{x}{\selecte{\lambda x.e}}{c}
    \ALT \updatee{\lambda x.e_1}{\lambda x.e_2}\\
&&&&\ALT \foreache{x}{\lambda y.\lambda z. c} 
    \ALT \foreachr{s_1}{s_2}{\lambda x.\lambda y. e}\\
&&&&\ALT \txn{i}{\I_e,\I_c}{ c } \ALT \ctxn{i}{\I_e,\I_c,\stl,\stg}{c} \ALT c1 || c2\\
% t & \in & \mathtt{Terms} & \coloneqq & e \ALT c\\
\ectx & \in & \mathtt{Eval\;Ctx} & ::= & \bullet \ALT  
  \bullet || c_2 \ALT c_1 || \bullet \ALT \bullet;\,c_2 
  \ALT \ctxn{i}{\I_e,\I_c,\stl,\stg}{\bullet} \\
\end{array}
\end{smathpar}
%
\bigskip

@@

\begin{minipage}{2.8in}
\rulelabel{E-Seq1}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \stg \vdash (c1, \stl) \stepsto (c1', \stl') \spc c1 \neq \cskip
}
{
  \stg \vdash (c1;c2, \stl) \stepsto 
              (c1';c2,\stl')
}
\end{array}
\end{smathpar}
\end{minipage}

\begin{minipage}{2.8in}
\rulelabel{E-Seq2}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \stg \vdash (c1, \stl) \stepsto (\cskip, \stl')
}
{
  \stg \vdash (c1;c2, \stl) \stepsto 
              (c2,\stl')
}
\end{array}
\end{smathpar}
\end{minipage}

\begin{minipage}{2.8in}
\rulelabel{E-IfTrue}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \eval(e) = \C{true}
}
{
  \stg \vdash (\ite{e}{c_1}{c_2}, \stl) \stepsto 
              (c1,\stl)
}
\end{array}
\end{smathpar}
\end{minipage}

\begin{minipage}{2.8in}
\rulelabel{E-IfFalse}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \eval(e) = \C{false}
}
{
  \stg \vdash (\ite{e}{c_1}{c_2}, \stl) \stepsto 
              (c2,\stl)
}
\end{array}
\end{smathpar}
\end{minipage}

@@

\begin{center}
\begin{minipage}{3in}
\rulelabel{E-Commit}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \I_c\,\,(\stl,\stg,\stg')
}
{
  (\ctxn{i}{\I_e,\I_c,\stl,\stg}{\cskip},\stg') \stepsto (\cskip,\stl\gg\stg')
}
\end{array}
\end{smathpar}
\end{minipage}
\end{center}
\hfill
%
\caption{\small \txnimp: Syntax and Small-step semantics}
\label{fig:txnimp}
\end{figure*}

\begin{figure}[t]
\raggedright
%
\textbf{Txn-Local Reasoning} \quad 
  \fbox {\( R \vdash \hoare{P}{c}{Q} \)} \\
%\fbox{\( \rg{\mathbb{I},P,R}{\txnbox{c}_i}{G,Q}\)} \quad
%\fbox{\( \rg{\mathbb{I},P,R}{c}{G,Q}\)} \quad\\
%
\begin{minipage}{3.2in}
\rulelabel{RG-Insert}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,P)\\
  \hspace*{-1.1in}\forall\stl,\stl',\stg,i.~P(\stl,\stg) \conj i \not\in
  \dom(\stl\cup\stg) \\
  \conj \stl'=\stl \cup 
  \{\{\bar{f}=x.\bar{f};\,\idf=i;\,\delf=\C{false}\} \Rightarrow 
  Q(\stl',\stg)
}
{
  R \vdash \hoare{P}{\inserte{x}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

%
\begin{minipage}{3.2in}
\rulelabel{RG-Delete}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,P)\\
  \hspace*{-0.2in}\forall\stl,\stl',\stg.~P(\stl,\stg) \conj 
  \stl' = \stl \cup \{r' \,|\, \exists(r\in\Delta).~ [r/x]e=\C{true} \\
        \hspace*{0.7in}\conj r'=\{\bar{f}=r.\bar{f}; \idf=r.\idf;
        \delf=\C{true}\}\}
  \Rightarrow 
  Q(\stl',\stg)
}
{
  R \vdash \hoare{P}{\deletee{\lambda x.e}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

%
\begin{minipage}{3in}
\rulelabel{RG-Update}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,P)\\
  \hspace*{-0.2in}\forall\stl,\stl',\stg.~P(\stl,\stg) \conj 
  \stl' = \stl \cup \{r' \,|\, \exists(r\in\Delta).~ [r/x]e_2 =\C{true} \\
        \hspace*{1.4in}\conj r'=[r/x]e_1\}
  \Rightarrow 
  Q(\stl',\stg)
}
{
  R \vdash \hoare{P}{\updatee{\lambda x.e_1}{\lambda x.e_2}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

%
\begin{minipage}{3in}
\rulelabel{RG-Select}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  R \vdash \hoare{P'}{c}{Q}\spc
  \stable(R,P)\\
  \hspace*{-0.2in}P'(\stl,\stg) \Leftrightarrow P(\stl,\stg) \wedge
  x = \{r' \,|\, \exists(r\in\Delta).~ [r/x]e_2 =\C{true}\} \\
}
{
  R \vdash \hoare{P}{\lete{y}{\selecte{\lambda x.e}}{c}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

%
\begin{minipage}{3in}
\rulelabel{RG-Foreach}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(\R,Q)\spc
  \stable(\R,\psi)\\
  P \Rightarrow [y/\phi]\psi\spc
  \R \vdash \hoare{\psi \wedge z\in x}{c}{Q_c}\\
  Q_c  \Rightarrow [y \cup \{z\} / y]\psi \spc
  [x / y]\psi \Rightarrow Q
}
{
  \R \vdash \hoare{P}{\foreache{x}{\lambda y.\lambda z.c}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

\begin{minipage}{3in}
\rulelabel{RG-Seq}
\begin{smathpar}
\begin{array}{c}
\RULE
{
\hoare{P} {c1} {Q^{'}} \spc \hoare{Q^{'}}{c2}{Q}\\
\stable(R, Q^{'})
}
{
  R \vdash \hoare{P}{c1;c2}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}

@@

\caption{\small \txnimp: Rely-Guarantee Rules}
\label{fig:rg-rules}
\vspace*{-12pt}
\end{figure}

\begin{definition}[ Step-indexed reflexive transitive closure]
For all $A:\text{Type}$, $R: A \rightarrow A \rightarrow \mathbb{P}$, and $n :
\mathbb{N}$, the step-indexed reflexive transitive closure $R^n$ of $R$ is
the smallest relation satisfying the following
properties:
\begin{itemize}
\item $\forall (x:A).\, R^0 (x,x)$
\item $\forall (x,y,z : A).\, R(x,y) \conj R^{n-1}(y,z) \Rightarrow
R^{n}(x,z)$
\end{itemize}
\end{definition}

@@

$$
\forall\stl,\stl',\stg,i.~P(\stl,\stg) \conj i \not\in
  \dom(\stl\cup\stg) \\
  \conj \stl'=\stl \cup 
  \{\{\bar{f}=x.\bar{f};\,\idf=i;\,\delf=\C{false}\} \Rightarrow 
  Q(\stl',\stg)
$$

@@

>>>>

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

%\documentclass[preprint,numbers]{sigplanconf}
\documentclass[acmlarge,anonymous]{acmart}\settopmatter{printfolios=true}

% The following \documentclass options may be useful:

% preprint      Remove this option only once the paper is in final form.
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% numbers       To obtain numeric citation style instead of author/year.

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{ifpdf}
\usepackage{graphicx}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{stmaryrd}
%\usepackage[numbers]{natbib}
\usepackage{amsthm}
\usepackage{listings}          % format code
\usepackage{wrapfig}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{color}
\usepackage{url}
\usepackage{tikz}
\usepackage{multirow,array}
%\usepackage{float}

\input{mydefs.tex}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother
%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
\acmYear{2017}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission
\setcopyright{none}             %% For review submission
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
% Uncomment the publication rights you want to use.
%\publicationrights{transferred}
%\publicationrights{licensed}     % this is the default
%\publicationrights{author-pays}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

\title{Alone Together:
  Compositional Reasoning and Inference for Weak Isolation}

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}
}
\email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{First2 Last2}
\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}
}
\email{first2.last2@inst2b.org}         %% \email is recommended

\maketitle
%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\section{Operational Semantics}

%\renewcommand{\ctxn}[3]{\C{TXN}_{#1}\langle #2 \rangle\{#3\}}
%\begin{figure*}[H]
%\raggedright
%
\textbf{Syntax}\\
%
\begin{smathpar}
\renewcommand{\arraystretch}{1.2}
\begin{array}{lclcl}
\multicolumn{5}{c} {
  {x,y} \in \mathtt{Variables}\qquad
  {f} \in \mathtt{Field\;Names} \qquad
% {\tau} \in \mathtt{Table\;Names}
  {i,j} \in \mathbb{N} \qquad
  {\odot} \in \{+,-,\le,\ge,=\}\qquad
  {k} \in \mathbb{Z}\cup\mathbb{B} \qquad
  {\rec} \in \{\bar{f}=\bar{k}\}\
}\\
{\stl,\stg,s} & \in & \mathtt{State} & \coloneqq &  \Pow{\{\bar{f}=\bar{k}\}} \\
{\I_e, \I_c }  & \in & \mathtt{Isolation Spec} & \coloneqq & (\stl,\stg,\stg') \rightarrow \Prop\\
v & \in & \mathtt{Values} & \coloneqq & k \ALT \rec \ALT s\\
e & \in & \mathtt{Expressions} & \coloneqq & k \ALT x \ALT x.f 
    \ALT \{\bar{f}=\bar{e}\} \ALT e_1 \odot e_2\\ 
c & \in & \mathtt{Commands} & \coloneqq & \cskip \ALT \lete{x}{e}{c}
    \ALT \ite{e}{c_1}{c_2}\ALT c_1;c_2 \ALT \inserte{x}  \\
&&&&\ALT \deletee{\lambda x.e}
    \ALT \lete{x}{\selecte{\lambda x.e}}{c}
    \ALT \updatee{\lambda x.e_1}{\lambda x.e_2}\\
&&&&\ALT \foreache{x}{\lambda y.\lambda z. c} 
    \ALT \foreachr{s_1}{s_2}{\lambda x.\lambda y. e}\\
&&&&\ALT \ctxn{i}{\I_e,\I_c}{ c } \ALT \ctxn{i}{\I_e,\I_c,\stl,\stg}{c} \ALT c1 || c2\\
% t & \in & \mathtt{Terms} & \coloneqq & e \ALT c\\
\ectx & \in & \mathtt{Eval\;Ctx} & ::= & \bullet \ALT  
  \bullet || c_2 \ALT c_1 || \bullet \ALT \bullet;\,c_2 
  \ALT \ctxn{i}{\I_e,\I_c,\stl,\stg}{\bullet} \\
\end{array}
\end{smathpar}
%
\bigskip

@@

\begin{minipage}{2.8in}
\rulelabel{E-Seq1}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \stg \vdash (c1, \stl) \stepsto (c1', \stl') \spc c1 \neq \cskip
}
{
  \stg \vdash (c1;c2, \stl) \stepsto 
              (c1';c2,\stl')
}
\end{array}
\end{smathpar}
\end{minipage}
\begin{minipage}{2.8in}
\rulelabel{E-Seq2}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \stg \vdash (c1, \stl) \stepsto (\cskip, \stl')
}
{
  \stg \vdash (c1;c2, \stl) \stepsto 
              (c2,\stl')
}
\end{array}
\end{smathpar}
\end{minipage}

\begin{minipage}{2.8in}
\rulelabel{E-IfTrue}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \eval(e) = \C{true}
}
{
  \stg \vdash (\ite{e}{c_1}{c_2}, \stl) \stepsto 
              (c1,\stl)
}
\end{array}
\end{smathpar}
\end{minipage}
\begin{minipage}{2.8in}
\rulelabel{E-IfFalse}
\begin{smathpar}
\begin{array}{c}
\RULE
{
 \eval(e) = \C{false}
}
{
  \stg \vdash (\ite{e}{c_1}{c_2}, \stl) \stepsto 
              (c2,\stl)
}
\end{array}
\end{smathpar}
\end{minipage}

@@

\begin{center}
\begin{minipage}{3in}
\rulelabel{E-Commit}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \I_c\,\,(\stl,\stg,\stg')
}
{
  (\ctxn{i}{\I_e,\I_c,\stl,\stg}{\cskip},\stg') \stepsto (\cskip,\stl\gg\stg')
}
\end{array}
\end{smathpar}
\end{minipage}
\end{center}
\hfill
%
%\caption{\small \txnimp: Syntax and Small-step semantics}
%\label{fig:txnimp}
%\end{figure*}

\section{Rely-Guarantee Reasoning}

%\begin{figure}[t]
%\raggedright
%
\textbf{Txn-Local Reasoning} \quad 
  \fbox {\( R \vdash \hoare{P}{c}{Q} \)} \\
%\fbox{\( \rg{\mathbb{I},P,R}{\txnbox{c}_i}{G,Q}\)} \quad
%\fbox{\( \rg{\mathbb{I},P,R}{c}{G,Q}\)} \quad\\
%
\begin{minipage}{0.5\textwidth}
\rulelabel{RG-Insert}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,P)\\
  \hspace*{-1.1in}\forall\stl,\stl',\stg,i.~P(\stl,\stg) \conj i \not\in
  \dom(\stl\cup\stg) \\
  \conj \stl'=\stl \cup 
  \{\{\bar{f}=x.\bar{f};\,\idf=i;\,\delf=\C{false}\} \Rightarrow 
  Q(\stl',\stg)
}
{
  R \vdash \hoare{P}{\inserte{x}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\rulelabel{RG-Delete}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,P)\\
  \hspace*{-0.2in}\forall\stl,\stl',\stg.~P(\stl,\stg) \conj 
  \stl' = \stl \cup \{r' \,|\, \exists(r\in\Delta).~ [r/x]e=\C{true} \\
        \hspace*{0.7in}\conj r'=\{\bar{f}=r.\bar{f}; \idf=r.\idf;
        \delf=\C{true}\}\}
  \Rightarrow 
  Q(\stl',\stg)
}
{
  R \vdash \hoare{P}{\deletee{\lambda x.e}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

%
\begin{minipage}{3in}
\rulelabel{RG-Update}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(R,P)\\
  \hspace*{-0.2in}\forall\stl,\stl',\stg.~P(\stl,\stg) \conj 
  \stl' = \stl \cup \{r' \,|\, \exists(r\in\Delta).~ [r/x]e_2 =\C{true} \\
        \hspace*{1.4in}\conj r'=[r/x]e_1\}
  \Rightarrow 
  Q(\stl',\stg)
}
{
  R \vdash \hoare{P}{\updatee{\lambda x.e_1}{\lambda x.e_2}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
\begin{minipage}{3in}
\rulelabel{RG-Select}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  R \vdash \hoare{P'}{c}{Q}\spc
  \stable(R,P)\\
  \hspace*{-0.2in}P'(\stl,\stg) \Leftrightarrow P(\stl,\stg) \wedge
  x = \{r' \,|\, \exists(r\in\Delta).~ [r/x]e_2 =\C{true}\} \\
}
{
  R \vdash \hoare{P}{\lete{y}{\selecte{\lambda x.e}}{c}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
%

%
\begin{minipage}{3in}
\rulelabel{RG-Foreach}
\begin{smathpar}
\begin{array}{c}
\RULE
{
  \stable(\R,Q)\spc
  \stable(\R,\psi)\\
  P \Rightarrow [y/\phi]\psi\spc
  \R \vdash \hoare{\psi \wedge z\in x}{c}{Q_c}\\
  Q_c  \Rightarrow [y \cup \{z\} / y]\psi \spc
  [x / y]\psi \Rightarrow Q
}
{
  \R \vdash \hoare{P}{\foreache{x}{\lambda y.\lambda z.c}}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}
\begin{minipage}{3in}
\rulelabel{RG-Seq}
\begin{smathpar}
\begin{array}{c}
\RULE
{
\hoare{P} {c1} {Q^{'}} \spc \hoare{Q^{'}}{c2}{Q}\\
\stable(R, Q^{'})
}
{
  R \vdash \hoare{P}{c1;c2}{Q}
}
\end{array}
\end{smathpar}
\end{minipage}

@@

%\caption{\small \txnimp: Rely-Guarantee Rules}
%\label{fig:rg-rules}
%\vspace*{-12pt}
%\end{figure}

\section{Soundness of RG-Reasoning}
\begin{definition}[ Step-indexed reflexive transitive closure]
For all $A:\text{Type}$, $R: A \rightarrow A \rightarrow \mathbb{P}$, and $n :
\mathbb{N}$, the step-indexed reflexive transitive closure $R^n$ of $R$ is
the smallest relation satisfying the following
properties:
\begin{itemize}
\item $\forall (x:A).\, R^0 (x,x)$
\item $\forall (x,y,z : A).\, R(x,y) \conj R^{n-1}(y,z) \Rightarrow
R^{n}(x,z)$
\end{itemize}
\end{definition}

@@

$$
\forall\stl,\stl',\stg,i.~P(\stl,\stg) \conj i \not\in
  \dom(\stl\cup\stg) 
  \conj \stl'=\stl \cup 
  \{\{\bar{f}=x.\bar{f};\,\idf=i;\,\delf=\C{false}\} \Rightarrow 
  Q(\stl',\stg)
$$

@@

% We recommend abbrvnat bibliography style.

%\bibliographystyle{plainnat}
\small
\bibliography{all}

\end{document}
